### 2020-10-06 thesis/msc-thesis.tex
add content to sections with bullet points

\textbf{\large Master-Arbeit} % Bachelor-Arbeit

\vspace{0.5\baselineskip}
{\huge
\textbf{Titel}
}
\end{center}

@@

@@

@@

\section{(Beispiel) Netzwerke}
\label{sec:networks}

\section{(Beispiel) Informationsextraktion}
\label{sec:ie}

\section{Verwandte Arbeiten}
\label{sec:related}

>>>>

\textbf{\large Bachelor-Arbeit}

\vspace{0.5\baselineskip}
{\huge
\textbf{Messaging Architecture for Integration of Customer Self-Services}
}
\end{center}

@@

\begin{enumerate}
     \item Example(s) of CSS Problems Today
     \begin{enumerate}
          \item CSS incomplete in governmental administration
          \begin{enumerate}
               \item identity card renewal
               \item change of home address
               \item change of residency status 
          \end{enumerate}

          \item CSS incomplete in universities
          \begin{enumerate}
               \item transfer of profile: grades, certificates, etc. between universities
               \item applications in general (study place, semester abroad, ...)
          \end{enumerate}

          \item CSS different for each enterprise / organization
          \begin{enumerate}
               \item multiple identities
               \item multiple profiles => addresses, phone numbers, mail address
               \item time consuming to manage same information in all systems
          \end{enumerate}
     \end{enumerate}

     \item Solution for CSS Problems
     \begin{enumerate}
          \item One CSS providing company, which integrates multiple / all EA
          \item One identity, profile, address, phone number location
          \item Easy management of identity used by multiple enterprises / organizations
     \end{enumerate}

     \item Why is integration necessary?
     \begin{enumerate}
          \item Each enterprise / organization has its own identities, profiles, etc. in multiple systems
          \item The CSS providing company needs to manage those systems / data of each enterprise / organization
          \item Enterprise Integration solves this Problem
     \end{enumerate}

\end{enumerate}

@@

\begin{enumerate}
     \item What are challenges of integration?
     \begin{enumerate}
          \item Heterogeneous Enterprise Architecture Systems
          \begin{enumerate}
               \item Different Applications
               \item Different Application Vendors
               \item Different Application Interfaces
               \item No Application Interfaces
               \item Legacy Systems
          \end{enumerate}

          \item Different (proprietary) data models within and between Enterprises and Organizations

          \item Stability of Integration
          \begin{enumerate}
               \item Future Changes of EA
               \item Scalability
               \item Failure of EA or Integration Components
               \item ...
          \end{enumerate}

          \item Scarce Resources
          \begin{enumerate}
               \item Integration Development Speed
               \begin{enumerate}
                    \item Necessary Development <=> Reuse of existing Technology
                    \item Complexity / Size of Integration
               \end{enumerate}

               \item Maintenance of finished Integration

               \item Hardware / Software Costs of Integration
               \begin{enumerate}
                    \item Licenses for Software
                    \item Scalability of Integration => Necessary Computing Power
               \end{enumerate}

          \end{enumerate}

     \end{enumerate}

     \item How does the thesis solve the problems?
     \begin{enumerate}
          \item Messaging Integration
          \begin{enumerate}
               \item Loose Coupling
               \begin{enumerate}
                    \item Loose Coupling simplifies adaption to changing EA => simpler Maintenance
                    \item Loose Coupling simplifies integration of new EA systems => integration of heterogeneous EA
                    \item Loose Coupling allows Reuse of "Modules" => faster development
               \end{enumerate}

               \item Messaging enables communication with many systems through Adapters

               \item Messaging provides mechanisms for Stability
               \begin{enumerate}
                    \item Store-and-Forward
                    \item Load Balancing
               \end{enumerate}

          \end{enumerate}

          \item Integration Patterns
          \begin{enumerate}
               \item Patterns speed up construction of Integration Architecture
               \item Patterns are proven solutions
               \item Patterns abstract from possible technologies
               \begin{enumerate}
                    \item Simplifies understanding of integration concept
                    \item Allows implementation with different technologies
               \end{enumerate}

          \end{enumerate}

     \end{enumerate}

\end{enumerate}

@@

\section{Customer Self-Service}

\begin{enumerate}
     \item Definition of CSS
     \item What is CSS and why is it important?
     \item How to document CSS-Scenarios
     \item List of important CSS-Scenarios
     \begin{enumerate}
          \item Criteria for importance
     \end{enumerate}
\end{enumerate}

\section{Architecture Patterns}

\begin{enumerate}
     \item Definition
     \item Patterns relevant for CSS
     \item Relevant Architecture bricks and data bricks
\end{enumerate}

\section{Business Connector}

\section{Integration Patterns}
